\documentclass{beamer}
\usetheme{Cuerna}

\author{Alireza Arzehgar}
\title{GNU/Linux Users Group (LUG)}
\institute{Azad University of Mashhad}
\date{\today}

\begin{document}
	\begin{frame}[plain]
		\maketitle
	\end{frame}

	\begin{frame}
		\frametitle{What is GNU/Linux Users Group?}
		\begin{itemize}
			\pause
			\item What is GNU/Linux?
			\pause
			\item What is GNU/Linux distributoin?
			\pause
			\item How is GNU/Linux unique?

			\pause
			{\bfseries Free programmers are happy programmers are effective programmers}
			\pause
			\item What is user group?
			\pause
			\item Why has LUG become less fun?
			\pause
			\item How can we make LUG fun again?
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{What does a LUG do}
		\begin{itemize}
			\pause
			\item Advocacy
			\pause
			\item Education
			\pause
			\item Support
			\pause
			\item Socialising
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{GNU/Linux Advocacy}
		\begin{itemize}
			\pause
			\item Reason for our advocacy for GNU/Linux
			\pause
			\item The best OS!
			\pause
			\item The cost-free nature of GNU/Linux
			\pause
			\item Effective strategies for advocacy
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{GNU/Linux Education}
		\begin{itemize}
			\pause
			\item Help to universities
			\pause
			\item Help to tech companies
			\pause
			\item Help to people
			\pause
			\item Help to LUG
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{GNU/Linux Support}
		\begin{itemize}
			\pause
			\item Users
			\pause
			\item Consultants
			\pause
			\item Businesses, non-profit organisations, and schools
			\begin{itemize}
				\pause
				\item Support for using GNU/Linux in local businesses
				\pause
				\item Support for local software development for GNU/Linux
			\end{itemize}
			\pause
			\item Free/open-source software development
			\pause
			\item The GNU/Linux movement
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Consultants}
		\begin{itemize}
			\pause
			\item Gift culture
			\pause
			\item Invoice therapy
			\pause

			{\bfseries if your consulting advice is poorly heeded and poorly used,
			it just might be the case that you need to charge more}
			\pause
			\item When to refer a questioner to a consultant?
			\begin{itemize}
				\pause
				\item Seeking "recipe" solutions without learning fundamentals
				\pause
				\item Repeatedly asking the same or similar questions
				\pause
				\item Requesting private help in public forums
				\pause
				\item Giving vague or inconsistent problem descriptions
				\pause
				\item Interrupting answers with additional questions
				\pause
				\item Demanding quicker or reformulated responses
				\pause
				\item Asking overly complex or multipart questions
			\end{itemize}
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{GNU/Linux Socialising}
		\begin{itemize}
			\pause
			\item Have more fun
			\pause
			\item Acculturation
			\pause
			\item Learn GNU/Linux culture
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{LUG Activities}
		\begin{itemize}
			\pause
			\item Meetings
			\begin{itemize}
				\pause
				\item Technical presentations
				\pause
				\item Informal discussion groups
				\pause
				\item Online videoconferencing
				\pause
				\item User group business
				\pause
				\item GNU/Linux installation
				\pause
				\item Configuration and bug-squashing
				\pause
				\item Eat, drink, and be merry
			\end{itemize}
			\pause
			\item Online resources
		\end{itemize}
	\end{frame}

\end{document}
